Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-14 hscc2017/paper.tex
added Alessandro's comments back

The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time. 
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}

>>>>

\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}

\textcolor{green}{The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time}. 
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
\red{[what does this alpha-numerical code mean?]}
\textcolor{green}{CBMC (SHA-1 hash) version:} 7a6cec1dd0eb8843559591105235f1f2c4678801}
